Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2021-05-29 analysis/paper/asymsam.tex
Render

\begin{figure*}
\includegraphics{method-1} \caption{(ref:method-cap}\label{fig:method}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics{method-1} \caption{Spatial patterns of the first EOF of 700~hPa geopotential height for 1979 -- 2018 period. (a) Full field, (b) zonally asymmetric component and (c) zonally symmetric component. Arbitrary units; positive values in blue and negative values in red.}\label{fig:method}
\end{figure*}
